This is an example of article title

### 2021-10-08 paper/paper.tex
Changes to solve affiliation issues
Fix a missing file (for build)

The discipline of combinatorial optimization consists in finding an optimal configuration of elements within a finite set. Such a set is usually subject to constraints that can be represented by functions that are often highly combinatorial. These constraints are mostly formulated as concepts, boolean functions indicating whether each constraint is respected or not. A solution (sometimes called a satisfactory solution, depending on the domain) is a configuration that respects all the constraints.

@@

This work, consists in a library that implements ICNs in the Julia programming language \cite{bezanson2017julia}. Although we present a direct application of ICNs in the following subsection, this neural network framework is simple to extend to learn other combinatorial and non-combinatorial functions.

@@

All methods required for the definition of additional layers are all available. An (unweighted) ICN is simply generated from a sequence of layers. After a learning phase using the a genetic algorithm from \texttt{Evolutionary.jl}\footnote{\url{https://github.com/wildart/Evolutionary.jl}}, this ICN can output a composition in various forms.

@@

Note that from Julia \texttt{v1.7}, calling \texttt{using} on uninstalled package will prompt the user to install it. Hence, the last command is the only one strictly required.

@@

The \emph{AllDifferent} constraint ensures that all the values of a given configuration are unique.

>>>>

The discipline of combinatorial optimization consists in finding an optimal configuration of elements within a finite set. Such a set is usually subject to constraints that can be represented by functions that are often highly combinatorial. These constraints are mostly formulated as concepts, boolean functions indicating whether each constraint is respected or not. A solution (sometimes called a satisfying solution, depending on the field) is a configuration that respects all the constraints.

@@

This work consists in a library that implements ICNs in the Julia programming language \cite{bezanson2017julia}. Although we present a direct application of ICNs in the following subsection, this neural network framework is simple to extend to learn other combinatorial and non-combinatorial functions.

@@

All methods required for the definition of additional layers are all available. An (unweighted) ICN is simply generated from a sequence of layers. After a learning phase using a genetic algorithm from \texttt{Evolutionary.jl}\footnote{\url{https://github.com/wildart/Evolutionary.jl}}, this ICN can output a composition in various forms.

@@

Note that from Julia \texttt{v1.7}, calling \texttt{using} on an uninstalled package will prompt the user to install it. Hence, the last command is the only one strictly required.

@@

The \emph{AllDifferent} constraint ensures that all the values of a given configuration are unique. This constraint is representative of Constraint Programming and is used in a large amount of models.
